Fire Probability
========================================================

```{r}
omnr <- read.csv("OMNR_data.csv") # load OMNR dataset

attach(omnr)

# Clean dataset = Only fires in the Measured and Intensive Zones + caused = Lightening

omnr.zones <- subset(omnr, subset = (omnr$FIRE_MGT_ZONE == "MEA" | omnr$FIRE_MGT_ZONE == "INT") & omnr$GENERAL_CAUSE == "LTG") 

# Calculate the number of fires that escape Initial Attach fire Suppression

Et.MEA  <- (sum(omnr$FINAL_SIZE > 3 & omnr$FIRE_MGT_ZONE == "MEA"))
Et.INT  <- (sum(omnr$FINAL_SIZE > 3 & omnr$FIRE_MGT_ZONE == "INT"))

# Calculate the number of escaped fires that grow to become large (>200ha) fires

Lt.MEA  <- (sum(omnr$FINAL_SIZE > 200 & omnr$FIRE_MGT_ZONE == "MEA"))
Lt.INT  <- (sum(omnr$FINAL_SIZE > 200 & omnr$FIRE_MGT_ZONE == "INT"))

# Calculate the propability of an escaped fire becoming a large fire

pt.MEA <- Lt.MEA / Et.MEA
pt.INT <- Lt.INT / Et.INT
```

Display probability of an escaped fire becoming a large fire in Measured Zone

```{r}
show(pt.MEA)
```

Display probability of an escaped fire becoming a large fire in Intensive Zone

```{r}
show(pt.INT)
```

Therefore, the probability of an escaped fire becoming a large fire in Measured Zone is approximately twice that of the probability in the Intensive Zone (i.e., 24% vs 10%). This is what one would expect if more aggressive fire suppression is effective at reducing the number of very large fires.

### Session info:

```{r session-info}
print(sessionInfo(), locale=FALSE)
```
